Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-04 manuscript.tex
Clarify 'how many acini per lung' we chose [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591/checks
https://github.com/habi/acinar-analysis-manuscript/runs/401056157

\emph{A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}}.
\emph{This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/commit/c56a516d2a7b3c0eec6f0b820c5d8744313bc31b...baed3cc09e71d256087e8856d8e2db5d7d542e75}{has been updated} since the original submission}.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/baed3cc09e71d256087e8856d8e2db5d7d542e75/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/baed3cc09e71d256087e8856d8e2db5d7d542e75}{habi/acinar-analysis-manuscript@baed3cc}
on December 4, 2020.

@@

This semi-automatic acinus segmentation method was applied to lung samples obtained throughout lung development, at postnatal days 4, 10, 21 and 60.
In total we extracted 701 acini from 12 animals.
Even if our method is efficient, we could not have stereologically assessed all these 701 acini, we thus performed a subsampling and stereologically analyzed 268 acini, as specified in the section below.

>>>>

\emph{A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/786681} and has been submitted to the \href{https://journals.physiology.org/journal/ajplung}{\emph{American Journal of Physiology - Lung Cellular and Molecular Physiology}}}.
\emph{This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/commit/c56a516d2a7b3c0eec6f0b820c5d8744313bc31b...e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591}{has been updated} since the original submission}.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/e0a6b5fb8ba2cead74aa2be2fa4e0cec35c58591}{habi/acinar-analysis-manuscript@e0a6b5f}
on December 4, 2020.

@@

This semi-automatic acinus segmentation method was applied to lung samples obtained throughout lung development, at postnatal days 4, 10, 21 and 60.
In total we extracted 701 acini from 12 animals, a breakdown of the number of extracted and assessed acini per animal is given in \ref{tbl:counts}.
Even if our method is efficient, we could not have stereologically assessed all these 701 acini, we thus performed a subsampling and stereologically analyzed 268 acini, as specified in the section below.
